Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
reverted changed variable name in case study, wip edits in sec 7

\begin{lstlisting}[style=default]
(def mean-office-distance
     "average time to arrive"
     10.)
(def sd-time-to-arrive
     "standard deviation of arrival time"
     3.)
(def time-sd
     "walking time deviation"
     1.)
\end{lstlisting}

@@

Compilation of Anglican into Clojure is built around a variant of CPS
transformation. In a basic CPS-transformed program, a
continuation receives a single argument --- the computed value.
In Anglican, there are two flows of computation going in
parallel: values are computed by functional code, and,
at the same time, the state of the probabilistic program,
used by inference algorithms, is updated by
probabilistic forms. Because of that, in Anglican a continuation
accepts  \textit{two} arguments:
\begin{itemize}
    \item the computed value;
    \item the internal state, bound to the local variable
        \texttt{\$state} in every lexical scope.
\end{itemize}

>>>>

\begin{lstlisting}[style=default]
(def mean-time-to-arrive
     "average time to arrive"
     10.)
(def sd-time-to-arrive
     "standard deviation of arrival time"
     3.)
(def time-sd
     "walking time deviation"
     1.)
\end{lstlisting}

@@

Anglican queries are compiled into Clojure using a variant of CPS
transformation. In a basic CPS-transformed program, a
continuation receives a single argument --- the computed value.
In Anglican, two flows of computation are performed in
parallel: values are computed by functional code, and,
at the same time, the state of the probabilistic program,
used by inference algorithms, is updated by
probabilistic forms. Because of that, in Anglican a continuation
accepts  \textit{two} arguments:
\begin{itemize}
    \item the computed value;
    \item the internal state, bound to the local variable
        \texttt{\$state} in every lexical scope.
\end{itemize}
